The Weakly Nonlinear Magnetorotational Instability in a thin-gap Taylor Couette flow

### 2016-10-03 paper/thingap_mri_paper.tex
IVP figures added to thingap paper

>>>>

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{../figures/IVP_plot_thingap_AA_phase_2lambdacrit_2.png}%{allorders_velocity.eps}
\caption{IVP for two critical wavelengths.}\label{fig:IVP_2lambdacrit}
\end{figure*}

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{../figures/IVP_plot_thingap_AA_phase_2lambdacrit_10.png}%{allorders_velocity.eps}
\caption{IVP for 10 critical wavelengths.}\label{fig:IVP_10lambdacrit}
\end{figure*}
